---
title: "Lab 3 Functions and Vectors"
author: "Akash Agrawal Bejarano"
date: "2/1/2023"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

````{r}
library(tidyverse)
```

```{r}
V <- c("Bears", "Lions", "Dolphins", "Eagles", "Bengales")
```


## Question 1

An atomic vector is a collection of "things" that are of the same type. Looking at the vector V above we can see that this is a collection of words, specifically a collection of strings. Because all of these "things" are of the same type then we can say that vector V is an atomic vector. 

## Question 2

```{r}
V[3]
```

## Question 3

```{r}
V[c(1,3,5)]
```

## Question 4

```{r}
V[-1]
V[V == "Lions" | V == "Dolphins" | V == "Eagles" | V == "Bengales"]
```

## Question 5

```{r}
K <- list( x = 3:7, "never", 43, y = list(10,20,30))
```

The vector above is a list, as a list is heterogeneous. It is a collection of "things" that does not have to be of the same type, such as the one above. It is a vector that contains different types of objects. 

```{r}
str(K)
```

## Question 6 

```{r}
length(K)
```

## Question 7

```{r}
K[4]
```

## Question 8

```{r}
str(K[ ])
```

## Question 9

```{r}
tribble( ~x,    ~y,    ~w,    ~z,
              210,   300,   220,   180,
              102,   100,   119,   187,
              176,   175,   188,   173,
              87,    95,   91,     94,
              202,   210,  234,    218,
              110,   122,  131,    128,
) -> dt
dt
```

Part A)

```{r}
map_dbl(dt, mean)
```

Part B)

```{r}
map_dbl(dt, sd)
```

Part C)

```{r}
dt %>% map(~. ** (1/2))
```

Part D)

```{r}
summary(dt)
```

## Question 10

```{r}
x <- list(26, 32, 45, 50, 65, 77, 82)
y <- list(30, 43, 50, 58, 62, 71, 88)
```

Part A) 

```{r}
test <- Map('+', x, y)
test
```

Part B) 

```{r}
x1 <- x %>% map(~. ** 2)
y1 <- y %>% map(~. ** (1/2))
test <- Map('-', x1, y1)
test
```

Part C) 

```{r}
x2 <- x %>% map(function(x) log10(x))
y2 <- y %>% map(function(y)log(y))
test <- Map('/', x2, y2)
test
```
